LAGOS lake depth

### 2020-01-07 tables/01_predictors.Rmd
cleanup

# dt <- mutate(dt, pretty = case_when(
#   nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
#   TRUE ~ pretty), 
#   IQR = paste0(q25, " - ", q75))
# dt <- dplyr::select(dt, Variable = pretty, 
#                     Median = q50, Q25 = q25, Q75 = q75)

>>>>

# dt <- mutate(dt, pretty = case_when(
#   nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
#   TRUE ~ pretty), 
#   IQR = paste0(q25, " - ", q75))
dt <- dplyr::select(dt, variable, # Variable = pretty,
                    Median = q50, Q25 = q25, Q75 = q75, n)
